\documentclass{report}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{biblatex}
\renewcommand{\baselinestretch}{1.25}
\newcommand\norm[1]{\left\lVert#1\right\rVert}

\addbibresource{Stopeight_Analyzer.bib}
\iffalse
\bibliography{Stopeight_Analyzer}{}
\bibliographystyle{plain}
\fi

\begin{document}
\title{Stopeight Analyzer}
\author{Fassio Blatter}
\maketitle

\chapter{Introduction}
The main algorithm in this text is the Analyzer. It has been developed during the years 2009 to 2016 by Specific Purpose Software GmbH. It is now open sourced, but mostly exists in the form of code fragments.\\
This file is in the Stopeight repository on Github. Please edit here:\\
\href{https://github.com/specpose/stopeight/tree/master/doc/latex/Stopeight_Analyzer.tex}{https://github.com/specpose/stopeight/tree/master/doc/latex/Stopeight\_Analyzer.tex}\\
The DOI can be found here ~\cite{Stopeight}.\\
A brief overview can be found here:\\
\href{https://www.stopeight.com/dev_analyzer.html}{https://www.stopeight.com/dev\_analyzer.html}\\\\
The purpose of the Analyzer is to find intervals in a Vector Graph and produce an approximation. The input Vector Graph may be obtained from the Grapher, or it may be present in another mathematical context. Certain properties, such as the maximum derivative or the quantity or quality of measure spaces involved, are inherited from this context.\\\\
Preliminary: Grapher can turn a time-variant (or time-invariant) series/signal $s(x)$ into a Vector Graph $\mathbb{R}^2$. The scaling can be adjusted. An average can be used. More complex scenarios may be considered, where Spirals are removed, the number of 8's are limited or the signal is resampled.
\begin{equation}
vectorgraph: \mathbb{R} \rightarrow \mathbb{R}^2
\end{equation}
The Arcs $A \subset \mathbb{R}^2$ are an approximation of a Vector Graph $X \subset \mathbb{R}^2$:
\begin{align}
f \circ g: X \rightarrow A
\end{align}
\begin{equation*}
1 < card(X) < \infty
\end{equation*}
via the intermediate functions $f,g$ where the intermediate transversality $Y = X \cap A$ defines Arcs $U_{m}$. ~\cite[\nopp 9.9]{Loring} ($f \circ g$ is neither injective nor surjective) ~\cite[\nopp 2.1]{LauresSzymik}:
\begin{align}
f: X \approx B \rightarrow Y; g: Y \rightarrow A
\end{align}
Note: The set of Arcs A is a dim 1-manifold. In $A$ we can find a system of open sets. The set of charts $\{U_{m}\}$ covering the whole manifold $A$ is an atlas. ~\cite[\nopp 3.1.1.]{Fomenko} ~\cite[\nopp 4.5]{Wall} ($X$ is formally a discrete / dim 0-manifold)
\begin{align}
A = \cup_{m}U_{m}; (X = \cup_{n}V_{n})\\
Y: \text{0-submanifold} \Rightarrow (dim(X)=0)<(codim(Y)=1) \Rightarrow X \text{ disjoint } A
\end{align}
but
\begin{align}
Y: \text{0-submanifold} \Rightarrow (dim(B)=1)=(codim(Y)=1) \Rightarrow B \text{ joint } A
\end{align}
\iffalse
Within $f$ we are assigning a sequence of three points to compact Hausdorf invervals ~\cite[\nopp 6.1.3.]{Mortad}:
\begin{equation}
\{x_{n}\}_{n \in \mathbb{N}} \mapsto \{S,C,E\}
\end{equation}\\
\fi
The approximation aims to find the maximal smooth atlas. Each chart $U_{m}$ has a start of Turn $T \ni S = \min \limits _{U_{m}}$, a Corner $C \in U_{m}$ and an end of Turn $T \ni E = \max \limits _{U_{m}}$. This format has the benefit of reducing the amount of data for $Comparison$ (see Stopeight Comparator), while preserving the $Representation$ using quadratic bezier splines.

\chapter{Representation}

The affine transformations $q$ are functions that map to control points $Q \subset \mathbb{R}^2$:
\begin{align}
q: S \times C \times E \rightarrow Q\\
Q \cap X = 0; Q \cap Y = 0
\end{align}
The combination $M = Y \cup Q$ has parts from the original $X$'s, and constructed $Q$'s that are not in $A$ $\footnote{insertion: $C \notin X$, otherwise: $C \in X \cap A$}$:
\begin{align*}
S,C,E \in X; Q \setminus A=\{q_{1}(S,C,E),q_{3}(S,C,E),q_{4}(S,C,E),q_{6}(S,C,E)\}
\end{align*}
and is composed of four quadratic bezier splines $\gamma_{H}(t)$:
\begin{align}
\gamma_{H}: \mathbb{R} \rightarrow \mathbb{R}^2; t \mapsto (x,y)
\end{align}
with control point sets $\{H_{1},...,H_{4}\}$ per chart of M. The Arc segment defining function $\xi$ forms the planar coordinates $(x',y')$ of Arc $U_{m}$:
\begin{equation}
\xi: \mathbb{R} \rightarrow A; t \mapsto (x,y)
\end{equation}
\begin{align*}
\xi(t) =
\begin{cases}
\gamma_{H_{1}}(t); H_{1}=\{S,q_{1}(S,C_{1},E),q_{2}(S,C_{2},E)\} & t \in [0,\frac{1}{4}]\\
\gamma_{H_{2}}(t); H_{2}=\{q_{2}(S,C_{2},E),q_{3}(S,C_{1},E),C_{3}\} & t \in [\frac{1}{4},\frac{1}{2}]\\
\gamma_{H_{3}}(t); H_{3}=\{C_{3},q_{4}(S,C_{1},E),q_{5}(S,C_{2},E)\} & t \in [\frac{1}{2},\frac{3}{4}]\\
\gamma_{H_{3}}(t); H_{4}=\{q_{5}(S,C_{2},E),q_{6}(S,C_{1},E),E\} & t \in [\frac{3}{4},1]
\end{cases}
\end{align*}
Note: The continuous function $\xi$ makes the topological space $A$ path-connected. Therefore it is a $path$ from $U_{m}$ to $U_{m+1}$ and intersects at least once at the unilateral limit $S \cap E$. ($dim (U_{m} \cup U_{m+1}) \geq 1?)$. ~\cite[\nopp 6.1.3.]{Mortad}\\\\
In order to compare the length from $[a,b] \subseteq A$ with $[a.b] \subseteq X$, we have to connect all $P_{n}, P_{n+1} \in X$ with one linear bezier spline each, because $X$ is discrete:
\begin{align}
\iota: \mathbb{R} \rightarrow B; t \mapsto (x,y)\\
\iota_{X}(t) = \{ \gamma_{H}(t)\lvert H=\{P_{n},P_{n}+\frac{(P_{n+1}-P_{n})}{2},P_{n+1}; P_{n}, P_{n+1} \in X\}\}\\
dim(B)=1<codim(Y)=1 \Rightarrow B \text{ joint } A
\end{align}
Note: For both $B$ and $A$, the length of the curve is now independent of the choice of parameter on the curve. ~\cite[\nopp 1.1]{Taimanov}\\\\
The arc-length metric $d(a,b)$ turns both manifolds $A$ and $B$ into metric spaces $(A,d)$ and $(B,d)$. ($\frac{d}{dt}$. ~\cite[\nopp 1.1.3]{Klingenberg}
\begin{equation}
d(a,b) = \int \limits _{a}^{b}\lvert \frac{\mathrm{d}}{\mathrm{d}t}\gamma(t)\rvert \mathrm{d}t
\end{equation}
We can now establish an injective $link$ between elements of $B$ and $A$. ($X \rightarrow A$ is injective, $but$ $A \rightarrow X$ is not accurate):
\begin{equation}
link: B \rightarrow A, (x,y) \mapsto (x',y'); link^{-1}: A \rightarrow B, (x',y') \mapsto (x,y)
\end{equation}

\chapter{Computation}

\section{Non-Oriented Segments}
Auxiliary functions are functions of the form $A,B \times A,B \rightarrow \mathbb{R}$ that can be applied to any segment $[a,b] \subseteq (B,d),(A,d)$ without any constraints.\\\\
The curve functions can be interprated as $\gamma(t,x(t),y(t))$. The derivative is the total derivative.
\begin{align}
\frac{\mathrm{d}}{\mathrm{d} t} \gamma (t) = \gamma(t) \begin{bmatrix} \underbrace{\frac{\partial}{\partial t} \mathrm{d} t}_{\text{is the same for } \xi \text{ and } \iota \text{because of the metric}} & \frac{\partial}{\partial x}  \mathrm{d} x & \frac{\partial}{\partial y} \mathrm{d} y \end{bmatrix} \frac{1}{\mathrm{d}t}
\end{align}\\
The direction of analysis $o$ is preserved in the sign for both straightness and curvature.
\begin{align}
o = \frac{(b-a)}{\lvert b-a \rvert}
\end{align}
The horizontal diameter is based on the metric of $\iota_{T}$.
\begin{equation}
diameter_{horiz,T}(a,b)= o \lvert \iota_{T}(b) - \iota_{T}(a) \rvert
\end{equation}

\subsection{Affine Transformation}
An affine transformation $M$ of a parametrised curve $\gamma_{H}$ with control points $\{h_{1},h_{2},h_{3}\} = H$ and parameter $t$:
\begin{equation}
transform(\gamma):
\begin{bmatrix}
1 & t & t^2
\end{bmatrix}
\underbrace{\begin{bmatrix}
1 & 0 & 0\\
-2 & 2 & 0\\
1 & -2 &1
\end{bmatrix}}_{Coefficients}
\begin{bmatrix}
Mh_{1} & Mh_{2} & Mh_{3}
\end{bmatrix}
=
\begin{bmatrix}
h_{1}' & h_{2}' & h_{3}'
\end{bmatrix}
\end{equation}
The composite $transform(\xi)$ is based on parameter $t$ and $\{H_{1}, ... ,H_{4}\}$.

\subsection{Legal Segment}
A legal segment is an affine transformtion of the arc curve function $transform(\xi) = \xi'$, so that all $\xi'_{y}(t)$ for $\xi'_{x}(t)$ are continuous (when):
\begin{align}
\xi'_{x}(a),\xi'_{y}(a), (\xi'_{y}(b)\text{ optional?}) = 0 \Leftrightarrow \iota'_{x}(a),\iota'_{y}(a), (\iota'_{y}(b)\text{ optional?}) = 0
\end{align}
(~\cite[\nopp Riemann Integrable?]{Widon})

\subsection{Straightness}
A straight line segment is determined by means of straightness.\\
The metric allows us to take the ratio of the difference of the jitter to the straight with $P_{n},P_{n+1} \in X$. \\
\begin{align}
straightness_{Rel}(a,b)=\frac{\int \limits _{a}^{b} \lvert \iota_{X}'(t) \rvert \mathrm{d}t}{diameter_{horiz,T}(a,b)}
\end{align}
A threshold can be chosen, which makes the segment straight or bent in A.\\
It is closely related to the curvature.
\subsubsection{Algorithm Version}
It is using Heron's formula for the area of a triangle in $P_{n}, P_{n+1},P_{n+2} \in [a,b] \subseteq X$.
\begin{align*}
\mathcal{A}=\lvert P_{i+1}-P_{i} \rvert\\
\mathcal{B}=\lvert P_{i+2} - P_{i+1} \rvert\\
\mathcal{C}=\lvert P_{i+2} - P_{i} \rvert\\
\mathcal{L}=\frac{\mathcal{A}+\mathcal{B}+\mathcal{C}}{2}\\
\mathcal{Q}=\sqrt{\mathcal{L}(\mathcal{L}-\mathcal{A})(\mathcal{L}-\mathcal{B})(\mathcal{L}-\mathcal{C})}
\end{align*}
to calculate the ratio of the areas in $A$ and lines in $B$.
\begin{align}
straightness_{Algo}(a,b)=o \sum_{i=0}^{n+2}\frac{\mathcal{Q}}{\mathcal{A}+\mathcal{B}}
\end{align}

\subsection{Curvature}
\iffalse
Because the diameter has to be calculated piece-wise, we have to set up a vector space with the turns $P_{n},P_{n+1} \in T$.
\begin{equation}
v \in (B,\norm{\cdot})
\end{equation}
Note: It is a Banach space.\\
\fi
Curvature is determined by the ratio of Area to Diameter.
\begin{align}
curvature_{Rel}(a,b) = \frac{\int \limits _{a}^{b} \lvert \xi'(t) \rvert \mathrm{d}t}{diameter_{horiz,T}(a,b)}
\end{align}
\subsubsection{Algorithm Version}
The sum of the pieces in the legal segment [a,b] with $P_{n}, P_{n+1} \in [a,b] \subseteq X$.
\begin{align}
curvature_{Algo}(a,b)= o \frac{\sum \limits _{i=0}^{n+1}y(P_{i})*(x(P_{i+1})-x(P_{i}))}{x(P_{n+1})-x(P_{0})}
\end{align}

\subsection{Corner}
A curvature is composed of an infinite amount of local maxima. Therefore the Corner in a section $[a,b] \subseteq B$ is:
\begin{equation}
C \ni \sup_{U}\lvert curvature(a,b) \rvert
\end{equation}
The indexing corresponds to the minimal grade of the polynomial that is necessary.
\begin{align}
C_{1} : \text{Quadratic Bezier Spline}\\
C_{2} \subset C_{1} : \text{Cubic Bezier Spline}\\
C_{3} \subset C_{2} \subset C_{1} : \text{Quartic Bezier Spline}
\end{align}
Note: Except for insertion (See Straight), $C_{3},C_{0} \in Y$, but all the others $C_{1},C_{2},C_{4},... \not\in X$, because they are only found in the approximation $C_{1},C_{2},C_{4},... \in A$.\\
(To be disclosed: Algorithms for finding lower Corner indexes from higher Corner indexes $q_{2},q_{5}$ and Control points inbetween $q_{1},q_{3},q_{4},q_{6}$)

\subsection{Turn}
A turn $T$ is a change of sign in the direction of the curve. In a segment $[a,b] \subseteq B$ an infinite amount of non-straight sections can be found.
\begin{equation}
T_{1} \ni \inf_{t \in U} \lvert \frac{\mathrm{d}}{\mathrm{d}t}\gamma(t) \rvert \approx 0
\end{equation}

\section*{Oriented Sections}
Sectioning/charting functions are functions of the form $(a,b) \mapsto (a,b')$ that can be applied to certain sections $[a,b] \subseteq (B,d),(A,d)$ with constraints of analytic priority. They create further sections of Turns $T$ in the transversality $Y$.

\section{Non-recursive Sections}
Non-recursive sections are not proper section types, but merely an expression of intermediate calculation and are therefore of medium analytic priority (See discussion of oriented submanifolds in Compact Covers). They do induce a shift inside the Compact Cover if they're not centered.\\\\
The $Max$ thresholds are reductions of different measure spaces. The $derivatives$ are affected by the thresholds.

\subsection{Cliff}
A Cliff is a section $[a,b']$ defined by a maximal curvature depending on the radius $r=diameter_{horiz,T}$. A single Cliff can have no more than the maximum curvature of a circle. It is a part of a Spiral.
\begin{align}
Max_{Curve}=\frac{(\pi r^2) /2}{2r}\\
C_{4} \ni b'
\end{align}
Measure Space: Curvature is no more than $(x')^2 + (y')^2 =1$  under any linear transformation of any segment and implies a reduction of the measure-spaces depending on scale.
\iffalse
\subsection*{Half Cliff}
Even though Half Cliffs are not being used, it is worth mentioning, that they produce Corners just to make the notation complete.
\begin{align}
Max_{Quarter}=\frac{((\pi-2) r^2) /4}{r}\\
C_{3} \ni b'
\end{align}
\fi

\subsection{Straight}
A Straight is a segment $[a,b]$ where $straightness(a,b)$ is smaller than the straightness of the unit circle (or straightness of exp?). It is a part of a Spike, or transfering the Straight half of a Dune to an adjacent ZigZag, or being used as part of Dune detection. A Corner is $inserted$ .
\begin{align}
Max_{Straight}=\\
C_{3} \ni \frac{b-a}{2}
\end{align}
A special case is when $card(U_{m})=2$, a Corner is inserted as well.\\\\
Measure Space: Straightness implies a reduction of the measure spaces depending on interval. $\mu$ which are smaller than the threshold.

\subsection{Swing}
A Swing is the section $[a,b']$ $\footnote{$a \in Y, b' \in A,B$ but it is not guaranteed, that $b' \in X$}$, where a legal segment $[a,b]$ is delimited by a sign change $[c,d]; c<b'<d$ under affine transformation $\xi'$. It is part of the Crest detection.\\
\begin{align}
\xi'(c)>0;\xi'(b')=0;\xi'(d)<0\\
T_{1} \ni b'
\end{align}
The criteria, whether a segment is within a chart is ~\cite[\nopp 20.7]{Loring}.
\begin{equation}
[a,b] \subseteq U_{m} \Rightarrow \exists  \xi(t) - \iota_{T}(t) >0 \land \nexists \xi(t) - \iota_{T}(t) \leq0
\end{equation}
(both vice-versa)

\subsection*{Absolute Differences}
Once these entities have been found, we can start to use absolute differences by means of setting the domain of $\iota$ to $T_{1},C_{4}$ and the domain of $\xi$ to $C_{3},C_{4}$ (and $C_{4}$?) unless noted otherwise.
\begin{align}
jitter(a.b)=\int \limits _{a}^{b}\lvert \iota_{X}(t) - \iota(t) \rvert \mathrm{d}t\\
area_{vert}(a,b)=\int \limits _{a}^{b} \lvert \xi(t)-\iota(t) \rvert \mathrm{d}t
\end{align}
\begin{align}
straightness_{Abs}(a.b)=\frac{jitter(a,b)}{diameter_{horiz,T}(a,b)}
\end{align}
\begin{align}
curvature_{Abs}(a,b) = \frac{area_{vert}(a,b)}{diameter_{horiz,T}(a,b)}
\end{align}
(Or if Corners are parametrised!! $P_{n},P_{n+1} \in C$ or $P_{n},P_{n+1} \in (C \cup T)$?)\\
(horizontals?)
\begin{align}
area_{horiz}(a,b)=\int \limits _{0}^{?} \lvert \xi(b-t)-\xi(a+t) \rvert \mathrm{d}t
\end{align}
(shaking?)
\begin{align}
diameter_{horiz,X}(a,b)=\int \limits _{0}^{?} \lvert \iota_{X}(b-t)-\iota_{X}(a+t)\rvert \mathrm{d}t
\end{align}
(different diameters?)
\begin{align}
diameter_{vert}=\text{Maximum}\\
diameter_{max}=\text{Star}
\end{align}

\subsection{Spike}
A Spike is a section $[a,b',c], where$
\begin{align}
straightness(a,b)\approx 1\\ curvature(a,b)>0
\end{align}
It is part of ZigZag detection.

\subsection{Dune}
A backside Dune $[a,b',c]$ is a section, where a non-Straight segment $[a,b']$ is followed by a Straight segment $[b',c]; $. It is part of the Edge detection.
\begin{align}
straightness(a,b')>Max_{Straight}\\ straightness(b',c)\leq Max_{Straight}
\end{align}

\section{Recursive Sections}
Derivatives are opening up interval-measure spaces. The maximum order of $derivatives$ is set by the scale-space. The scale-space depends on the maximal order of the polynomials considered. In the method discussed in this paper, they are quadratic (or quartic?).\\\\
The second order total derivative induces non-symetry.\\
(Binomial?)
\begin{align}
\frac{\mathrm{d}^2}{\mathrm{d}^2t}\gamma(t)=\partial^2 \gamma(t) \begin{bmatrix} \frac{\mathrm{d}^2x}{\partial^2 x} & 2 \frac{\mathrm{d}x\mathrm{d}y}{\partial x \partial y} & \frac{\mathrm{d}^2y}{\partial^2 y}\end{bmatrix}\frac{1}{\mathrm{d}^2t}
\end{align}
(Or Trinomial?)
\begin{align}
\frac{\mathrm{d}^2}{\mathrm{d}^2t}\gamma(t)=\partial^2 \gamma (t) \begin{bmatrix}\frac{\mathrm{d}^2 x}{\partial^2 x} & 2 \underbrace{\frac{\mathrm{d}t}{\partial t}}_{1} \frac{\mathrm{d}x}{\partial x} & 2 \frac{\mathrm{d}x\mathrm{d}y}{\partial x \partial y} & 2 \underbrace{\frac{\mathrm{d}t}{\partial t}}_{1} \frac{\mathrm{d}y}{\partial y} & \frac{\mathrm{d}^2 y}{\partial^2 y}\end{bmatrix}\frac{(\partial x + \partial y)^2}{\mathrm{d}^2 t}
\end{align}
The following non-symetric subsections reveal hidden second derivatives.
\begin{equation}
T_{2} \ni \inf_{t \in U} \lvert \frac{\mathrm{d}^2}{\mathrm{d}^2t}\gamma(t) \rvert \approx 0
\end{equation}

\subsection{Crest}
A backside Crest $[a,a']$ or $[a,b']$ is an iteration of:
\begin{enumerate}
\item The Forward direction of analysis of a $[a,b']$ Swing, followed by 
\item The Reverse direction of analysis $[b',a]$ reveals a Backward $[b',a']$ Swing
\end{enumerate}
The breaking condition is that no more entities are being found by either of the two steps.

\subsection{Edge}
A backside Edge $[a,b']$ is an iteration of:
\begin{enumerate}
\item A backside Dune $[a,b,c]$
\item A backside Dune $[c',b',a]$ 
\item A backside Dune $[a',b'',c']$...
\end{enumerate}
The breaking condition is that no more entities are being found after the second step.

\section{Compact Covers}
\subsubsection*{Open}
\begin{align}
A \text{ is open} \Leftrightarrow \inf_{A},\sup_{A}\in T_{0},C_{0}
\end{align}
In computer science there is the concept of the stream operator. This means that approximation $A$ would have to be recomputed whenever elements are added to the front or to the tail. Also it would require that a supremum arc length would have to be found from all the sections between turns $A \cap T$. It would make sense that the longest Spiral be chosen, which depends on curvature. One could also argue that the longest ZigZag with an absolute straightness of $1$ be chosen for the first center. Spreading out left and right, a mixed approach or a fully centered one could be chosen. One could also decide to interleave frontside and backside entities of the same type.
\subsubsection*{Closed}
\begin{align}
A \text{ is closed} \Leftrightarrow \min_{A},\max_{A}\in T_{0},C_{0}
\end{align}
For the time being, the approach in this paper is a compromise. Half-open front and tail sections $\footnote{It is questionable, whether losing front/tail sections is significant for most uses}$ are obliterated and the oriented manifolds between them are never fully centered. In particular the Crests and Edges exhibit a non-symetry, which significantly offset the consecutive oriented functions. Even finding Swings and Dunes shifts the adjacent entities. The reversal and priority of segments and sections imposes a certain rigor in programming techniques. A compatible software architecture is a requirement.\\
Nevertheless the curve can be interpreted, if a threshold in Stopeight Comparator is increased, which lowers the requirement for overlay comparison matching accuracy ($Comparator$).
It all comes down to whether oriented submanifolds are allowed and whether the enclosing submanifolds and the whole manifold are allowed to be oriented (Causal Structure).

\subsection{Spiral}
Spiral $\supset$ Cliff\\
A Spiral section $[a,b']$ is a Cliff, where
\begin{align}
Max_{Spiral}=\frac{curvature(a,b)}{\{n-m\in \mathbb{N} \vert U_{m},...,U_{n} \subseteq Spiral\}}\\
b' \in C_{4}
\end{align}
The Cliffs are centered outside in so that all cliffs in a spiral have the same curvature.\\\\
$C_{4}$ is the Corner of the Spiral section, but the Spiral as a whole also has Corners, which are indexed supremum norm of the curvature(?).
\subsection{ZigZag}
ZigZag $\supset$ Spike\\
A ZigZag [a,b'] is an iteration of:
\begin{enumerate}
\item A Spike $[a,b,c]$
\item A Spike $[a,b',c']$ and a Spike $[c',b'',c]$
\end{enumerate}
The breaking condition is when no more entities are being found.\\\\
Whether angles greater than 90 degree are allowed to be in the dataset is subject of definition.\\\\
Below 90 degree, it is not losing its orientation. Therefore it is a Corner indexed by the supremum norm of the curvature(?).\\
A single Spike section is in this case.
\begin{align}
b' \in C_{4}
\end{align}
From 90 degree to $\infty$, it is a Turn and is indexed by the infimum norm of the angle(?).\\
A single Spike section is in this case.
\begin{align}
b' \in T_{3} \Rightarrow \text{third derivative }= 0\text{?}
\end{align}
\subsection{Swell}
Swell $\supset$ Crest, Swell $\supset$ Swing, (Swell $\supset$ Dune?)

\chapter{Comparator}
(Formula are work in progress. The present state of the software implementation includes working overlay comparison.)\\\\
Please take note of the sign here. The difference of sign in the numerator and the denominator of area(?) indicate sign changes.\\
The alternating signs of times.
\begin{align}
s_{alt} = \sum_{\mu_{+}}^{}o -  \sum_{\mu_{-}}^{}o
\end{align}
The fliping signs of times across measure spaces?
\begin{equation}
s_{times} = \prod_{measures} o
\end{equation}

\subsection{Impulses}
Impulses are consecutive pulses of variable wavelengths which originate from the same source and are separated from other overlaping impulses.

\subsection{Imaginary Visibility}
Visibility is an increase of the polynomial (degree or coefficients?) of a curve segment.
When visibility is increased in a Spiral, it creates more subsegments. Points in $Y$ become uncertain at around $2\pi/3$. It is a Cantor-like diminishing isolation.\\
When curvature is decreased in a Spiral, it becomes a ZigZag.\\
When the direction of analysis is reversed, the curve areas lie on the other side, therefore the direction inverts the orientation of the curve segments. Their sign flips.
\begin{align}
\mu_{+}(\{[a,b] \subseteq A,B \vert \xi(t) -\iota_{T}(t)\geq0\})
\end{align}
Note: $\mu$ is a Lebesgue.
\begin{align}
visibility(a,b)=\prod_{\lvert \mu \rvert \approx (b-a)}^{}\frac{(\pi r^2) /2}{2r}-\mathcal{Q}\\
visibility(a,b)=\frac{s_{alt}}{\lvert s_{alt} \rvert} \sum_{}^{} curvature_{Abs}(a,b)\\
visibility(a,b)= \int \limits _{}^{}\xi_{C}(t)\mathrm{d}t(?)
\end{align}
\subsection*{Scale Space}
$arclength$ constant, $area$ grows, but $diameter$ constant.

\subsection{Real Isolation}
A lack of isolation is directly linked to the creation of more measure spaces.\\
If the sections are being extracted from left to right $[a,b];a<b$, isolation is positive. If the direction of analysis is reversed $[b,a]$, isolation is negative.\\
Opposite wave direction $\Leftrightarrow$ Negative Isolation.
\begin{align}
\eta_{+}=(\{[a,b] \subseteq A,B \vert a<b\}) \Leftrightarrow o=+1
\end{align}
Note: $\eta$ is a Lebesgue.
\begin{equation}
isolation(a,b)=o \prod_{\lvert \mu \rvert \approx (b-a)}^{} straightness_{Abs}(a,b)
\end{equation}
\subsection*{Interval Space}
$jitter$ grows, but $diameter$ constant.

\chapter{Separation}
The goal of separation is to find impulses or notes as they may be referred to in a musical context. It is important to note that the individual pulses have a causal relationship that connects them. Most oscillations are subject to amplitude and/or frequency-modulation, but they are usually repetitive, so they can be removed by statistical means. Truly random/stochastic signals on the other hand can not be filtered.

\subsection{Plancherel Theorem}
The main drawback of Fourier Transformation is that frames (integration bounds) and frequency window (measure) have to be adjusted. There are methods for finding orthogonal subspaces in frames. Fourier Transformation does fulfil the task of spectral separation, but it is not pulse-wise. The Plancherel Theorem connects the fields of frame-wise integration and periodic integration.\\\\
The method in this paper may provide a means of either finding exact frames (of length pulse or impulse?) in the original signal $s(x)$(See Grapher), or in the signal as in parametric curve differences of the type $\lvert \xi(t)-\iota_{T}(t) \rvert$ discussed in previous chapters.\\\\
Also Vector Graph manipulations such as scaling, resampling, finding/counting intersections, oriented section occurence requirements could yield interesting results.\\\\
A Polar to Cartesian Transform is a convolution with a sum of two fundamental numeric Taylor Series Expansions. Sine and Cosine functions are intrinsically linked to the quadratic entity $x^2 + y^2 =1$ and dividing the circle by four (90 deg.). Hyperbolic Sine is linked to $1/x$. The Polynomial encountered in the non-oriented (and oriented) Sections is of Grade 4. The character of quadratic polynomials is reflected in the limitations of the Fourier Transform.

\subsection{Spectral Separation}
For Swell/Crest.\\
There are two main criteria among which the waves can vary. The absolute indication for separation is visibility and isolation.\\
They occur periodically in a Swell.\\
In signal analysis, there is the notion of source separated and spectral separated pulses. Separation algorithms would benefit from an isolation parameter, indicating whether the pulses ...
The directed waves of straightness and curvature going forward/backward synchronously are periodic.
\begin{align}
z =  (\xi(t)-\iota_{X}(t))*(\cos{(visibility(a,b))} +\mathrm{i} \sin{(isolation(a,b))})(?)\\
\int \limits _{}^{} (\xi_{T}(t)-\iota_{T})*(\xi_{C}-\iota_{T})\mathrm{d}t=1(?)
\end{align}
\subsubsection{Resampling}

\chapter{Modeling}
(An attempt to extend the algebra to generic problems in physics.)\\\\
The complex conjugate is a manifestation of periodicity of two exact frames which are defined by something like a complex number:\\\\
The imaginary part is the other side of the wave vs\\
The imaginary part is the phase shift (fft)\\\\
(multiplication? addition?)
\begin{align}
A,B \times A,B \rightarrow \mathbb{C}\\
(a,b) \mapsto z\\
\end{align}
A complex norm $\norm{\cdot}$ is defined on the transversality (2).
\begin{align}
\norm{\cdot} : \mathbb{C} \rightarrow \mathbb{R}\\
\norm{z} = \sqrt{Re(z)^2+Im(z)^2}
\end{align}
Differential Equations?

\section{Wave Trains}
The mathematically most intriguing oriented submanifolds are Crests and Spikes. We introduce a mechanism for the annihilation and creation of pulses. Physical phenomena such as the creation of enthalpy and enthropy during phase transitions could be modeled. A Crest would appear in the outgoing phase when a signal of enthropy brakes in the corresponding medium of the carrier. A Spike is a beat that appears in joint states of crystal grids when the incoming phase accumulates in a $different$ medium.
Traveling wave trains are moving over stationary reef chains. Upon creation, enthropic wave trains are impulses, at the least even a part of a half-pulse (Example Spiral). Enthalpic reef chains change state when they are converted to a plasma state for an infinitesimal short period of time.\\\\
A wave train appears in a wave packet that splits up. A wave packet that splits, decreases its isolation and transfers a part of its visibility to the sub-wave packets. Depending on the wavelength of a Reef, the original wave packet may never appear again.\\\\
On the other hand, the sub-wave packets of an open ocean wave pick up wind. The enclosing wave packet can form a new wave train, together with neighbouring wave packets and so slowly, the little left-over, chaotic visibility of the sub-wave packets gets transferred not only to the enclosing wave packet, but to the whole wave train. The swell gets groomed and the short wavelengths disappear.\\\\
Because in any accurate measurement of matter, only a limited number of reef chains can be considered; For the multitude of periodic energy passing over a reef chain, all products of the chain are compared, up to the length of the frame of the train.
It could make sense to map such phenomena in a complex plane. Could we explain why for example a Crest starts appearing on a Reef, and different, purely imaginary waveforms appear in open ocean waters where waves travel in arbitrary directions.

\subsection{Wave Generation}
For Dune/Crest or Swing (stationary wave).\\
Supraliquid\\
Sail Effect / Surface Tension

\subsection{Phase Transitions}
For Dune/Spiral.
\begin{align}
z =  \sup_{U}\lvert curvature([a,b]) \rvert*(\cos{(isolation([a,b]))} +\mathrm{i} \sin{(visibility([a,b]))})
\end{align}

\subsection{Lightning}
For Spike/ZigZag.\\
Superconductor\\
If we're setting $\sqrt{1-y^2}$ to be the linear part of complex plane, $\phi$ in $z=\sqrt{1-y^2}e^{i\phi}$ is the rotational part.
\begin{align}
z =  straightness([a,b]) + \mathrm{i} curvature([a,b])
\end{align}

\subsection{Stateless}
Supercritical\\
gaseous/liquid carbondioxide

\printbibliography

\end{document}